%titolo{Happy Christmas – War Is over}
%autore{John Lennon}
%album{}
%tonalita{La}
%famiglia{Altre}
%gruppo{}
%momenti{}
%identificatore{happy_christmas}
%data_revisione{2012_06_24}
%trascrittore{Francesca Rossetti - Francesco Endrici}
\beginsong{Happy Christmas – War Is over}[by={Lennon}]
\beginchorus
And so this is \[A]Christmas \brk and what have you \[B-]done?
Another year \[E]over, a new one just \[A]begun;
And so this is \[D]Christmas, \brk I hope you have \[E-]fun
the near and the \[A]dear ones, \brk the old and the \[D]young.
A merry, merry \[G]Christmas, \brk and a happy New \[A]Year,
Let's hope it's a \[E-]good one, \[G] \brk without any \[D]fear \[E7]
\endchorus
\beginverse
And so this is \[G]Christmas \echo{War is over}
for weak and for \[A]strong \echo{if you want it}
The rich and the \[E-]poor ones \echo{war is over}
the road is so \[D]long. \echo{now}
And so, happy \[G]Christmas \echo{War is over}
for black and for \[A]white \echo{if you want it}
For the yellow and \[E-]red ones \echo{war is over}
Let's stop all the \[D]fights. \echo{now}
\endverse

\beginchorus
A merry, merry \[G]Christmas,\brk and a happy New \[A]Year,
Let's hope it's a \[E-]good one, \[G]\brk without any \[D]fear \[E7]
And so this is \[A]Christmas\brk and what have you \[B-]done?
Another year \[E]over,\brk a new one just \[A]begun;
And so this is \[D]Christmas,\brk we hope you have \[E-]fun
the near and the \[A]dear ones,\brk the old and the \[D]young.
A merry, merry \[G]Christmas,\brk and a happy New \[A]Year,
Let's hope it's a \[E-]good one, \[G]\brk without any \[D]fear \[E7]
\endchorus

\beginverse
And so this is ^Christmas \echo{War is over}
for weak and for ^strong \echo{if you want it}
The rich and the ^poor ones \echo{war is over}
the road is so ^long. \echo{now}
And so, happy ^Christmas \echo{War is over}
for black and for ^white \echo{if you want it}
For the yellow and ^red ones \echo{war is over}
Let's stop all the ^fights. \echo{now}
\endverse

\beginchorus
A merry, merry \[G]Christmas,\brk and a happy New \[A]Year,
Let's hope it's a \[E-]good one, \[G]\brk without any \[D]fear \[E7]
\[A]War is over, \[B-]if you want it \brk \[E]war is over \[A]now.
\endchorus
\endsong


